%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Technical Product Manager} % Job title
    {Iris Technology Corporation} % Organization
    {Irivne, CA} % Location
    {Apr. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pioneered the technical product manager role at Iris, coordinating the efforts of sales, business development, marketing, and engineering to create a uniform product vision for Iris' tactical power business unit.}
        \item {Developed the business cases, win-themes, and strategic positioning for business development opportunites in order to secure over \$6 million in revenue over the last year and add over \$20 million to the pipeline.}
        \item {Delivered successful proposal efforts by providing both technical expertise and compelling business narrative that emphasized customer needs.}
        \item {Transitioned opportunities from business development to the program management and engineering teams, ensuring that the customer's needs and use cases were well understood throughout the entire product development effort.}
        \item {Shaped product development efforts by creating user personas and market requirement documents for internal product development projects.}
        \item {Coordinated with the sales and marketing teams to define product positioning and messaging.}
        \item {Led rapid prototyping efforts to support the business development team. Participated heavily in sprint planning and prioritization of features to deliver the items most critical to securing the business.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineer} % Job title
    {Iris Technology Corporation} % Organization
    {Irvine, CA} % Location
    {Jun. 2015 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Significantly contributed to a number of programs in various engineering roles, including sales, software, systems, and project engineering.}
        \item {Strengthened relationships with US military customers by providing on-site technical integration support.}
        \item {Designed a desktop GUI application for internal product debugging that has become a standard template for desktop applications at Iris.}
        \item {Served as lead software engineer for multiple embedded software development efforts writing embedded C code for Cortex-M0 based microcontroller systems.}
        \item {Participated in an agile-based software development process both as a developer and as a stakeholder.}
        \item {Designed and implemented custom, interrupt-based, asynchronous drivers for single wire communciation protocols.}
        \item {Served as lead test engineer responsible for writing and performing product accpetance tests to validate system design requirements as part of Iris' AS9100D quality process.}
        \item {Served as acting program manager on programs exceeding \$500k in value, including internal and contract development efforts.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
